### 2023-01-31 manuscript.tex
avoid {{\_ bugs [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/8bbdd67883c9ed6306479264d368472288bd67d0.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/8bbdd67883c9ed6306479264d368472288bd67d0/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4056063800

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/91171dc6c031928ebbaa06767feaef4bcede30f4/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/91171dc6c031928ebbaa06767feaef4bcede30f4}{stain/2022-fdo-paper@91171dc}
on January 31, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/8bbdd67883c9ed6306479264d368472288bd67d0/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/8bbdd67883c9ed6306479264d368472288bd67d0}{stain/2022-fdo-paper@8bbdd67}
on January 31, 2023.
